Untargeted control doc

### 2023-10-06 untargeted/paruntargeted_control.Rmd
Saved GMP samples, done annotating

# polarity <- "pos"
polarity <- "neg"
# amendment <- "Amm"
# amendment <- "Nit"
# amendment <- "GMP"
amendment <- "Arg"
IS_type <- "noIS"
# IS_type <- "wIS"

@@

  } else if(polarity=="neg"){
    rescue_feats <- c(Bisulfate="FT0706", "Itaconic acid"="FT1544", 
                      "Salicylic"="FT1841")
  } else {
    stop("Unknown polarity")
  }
}
if(amendment=="GMP"){
  if(polarity=="pos"){
    rescue_feats <- c()
  } else if(polarity=="neg"){
    rescue_feats <- c()
  } else {
    stop("Unknown polarity")
  }
}
if(amendment=="Arg"){
  if(polarity=="pos"){
    rescue_feats <- c("FT0945", "FT1138", "FT1346", "FT1413", "FT1476",
                      "FT1505", "FT1533", "FT1935", "FT1945", "FT2029",
                      "FT2425", "FT2774", "FT2999", "FT3668")
  } else if(polarity=="neg"){
    rescue_feats <- c("FT0790", "FT1022", "FT1031", "FT1387")
  } else {
    stop("Unknown polarity")
  }
}

@@

```{r rescue feats rendering, eval=FALSE}
anno_manu <- readxl::read_excel("untargeted/manual_annotations.xlsx") %>%
  filter(amendment==!!amendment)
all_feat_data <- read_csv(paste0(output_folder, "all_feat_data.csv"))
anno_manu %>%
  filter(str_detect(notes, "[Rr]escue"))
all_feat_data %>%
  filter(mzmed%between%pmppm(138.9701 , 10))
```

>>>>

# polarity <- "pos"
polarity <- "neg"
# amendment <- "Amm"
# amendment <- "Nit"
amendment <- "GMP"
# amendment <- "Arg"
IS_type <- "noIS"
# IS_type <- "wIS"

@@

  } else if(polarity=="neg"){
    rescue_feats <- c(Bisulfate="FT0706", "Itaconic acid"="FT1544", 
                      "Salicylic"="FT1841")
  } else {
    stop("Unknown polarity")
  }
}
if(amendment=="GMP"){
  if(polarity=="pos"){
    rescue_feats <- c("FT1422", "FT1580", "FT1585", "FT1603", "FT3030")
  } else if(polarity=="neg"){
    rescue_feats <- c("FT0865")
  } else {
    stop("Unknown polarity")
  }
}
if(amendment=="Arg"){
  if(polarity=="pos"){
    rescue_feats <- c("FT0945", "FT1138", "FT1346", "FT1413", "FT1476",
                      "FT1505", "FT1533", "FT1935", "FT1945", "FT2029",
                      "FT2425", "FT2774", "FT2999", "FT3668")
  } else if(polarity=="neg"){
    rescue_feats <- c("FT0790", "FT1022", "FT1031", "FT1387")
  } else {
    stop("Unknown polarity")
  }
}

@@

```{r rescue feats rendering, eval=FALSE}
anno_manu <- readxl::read_excel("untargeted/manual_annotations.xlsx") %>%
  filter(amendment==!!amendment)
all_feat_data <- read_csv(paste0(output_folder, "all_feat_data.csv"))
anno_manu %>%
  filter(str_detect(notes, "[Rr]escue"))
all_feat_data %>%
  filter(mzmed%between%pmppm(111.0195 , 10))
```
